---
title: "4th valve location pattern for double horn"
author: "Yoshinobu Ishizaki"
date: last-modified
date-format: iso
format: 
  gfm:
    df-print: kable
---

```{r}
library(tidyverse)
```


## Create design pattern

Compared to 1-2-3 valves, 4th valve can be located at,

- thumb/pinkey finger side 
- inline/offset
- flat/step level

 and a valve rotation can be 
 
 - 90 degree
 - 60 degree
 - 120 degree
 
 Compose a table with these layout combinations.
 
```{r}
s1 <- c("thumb","pinkey")
s2 <- c("inline","offset")
s3 <- c("flat","step")
s4 <- c("90deg","60deg","120deg")
```

```{r}
v4tab <- expand_grid(s1,s2,s3,s4)
names(v4tab) <- c("Side","Align","Level","Rotation")
v4tab$Ex = ""
```

In case of 60 degree rotation, a valve does not have 2 levels, so that level difference is meaningless.

```{r}
v4tab <- 
  v4tab |> filter(!(Level == "flat" & Rotation == "60deg"))
```


## Existing example

There are some type of horn with one of such combination.

```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "thumb" & Align == "offset" & Level == "step"& Rotation == "60deg", "Alexander 103", Ex) )
```


```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "pinkey" & Align == "inline" & Level == "flat"& Rotation == "120deg", "Geyer; Yamaha 871", Ex))

```

```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "pinkey" & Align == "inline" & Level == "flat" & Rotation == "90deg", "Knopf; Paxman; E.Schmid", Ex))
```


```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "thumb" & Align == "offset" & Level == "step"& Rotation == "120deg", "Conn 8D; Yamaha 668-2; Hans Hoyer 6801", Ex))

```

```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "thumb" & Align == "offset" & Level == "step"& Rotation == "90deg", "Yamaha 868-1", Ex))

```

```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "thumb" & Align == "offset" & Level == "step"& Rotation == "90deg", "Kruspe; Klaus Fehr", Ex))

```


```{r}
v4tab <- 
  v4tab |> mutate(Ex = if_else(Side == "thumb" & Align == "inline" & Level == "flat" & Rotation == "90deg", "Yamaha 869", Ex))
```

## View table

```{r}
v4tab
```

So, out of 20 possible combinations, there are many unused pattern.

Can we create a new model to fill one of this? 


